---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  fig.width = 3,
  # fig.height = 3,
  dpi = 300,
  # out.width = "100%",
  message = FALSE
)
```

# arboretum

<!-- badges: start -->
<!-- badges: end -->

Plot customised phylogentic trees.

## Installation

You can install the latest version from [GitHub](https://github.com/) with:

``` r
if (!requireNamespace("devtools")) install.packages('devtools')
devtools::install_github("dkidney/arboretum", ref="main")
```

## Examples

Load the package (and check the version)

```{r}
library(arboretum)
packageVersion("arboretum")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	fig.asp = 0.6, 
	fig.width = 15, 
	out.width = "100%"
)
```

Plot a tree for a specific using the `taxon` argument. 

By default, any branch node ending in '-morpha', '-formes', '-oidea', '-idae', '-inae', '-ini' or '-ina' will be collapsed, unless you use the `collapse` argument to specify which taxa you wish to collapse.

Here are some examples.

```{r}
tree('tetrapodomorpha')
```

***

```{r}
tree('reptiliomorpha', collapse=c('diapsida', 'therapsida'), xmin=-345, xmax=-252)
```

***

```{r}
tree('therapsida', xmax=-200)
```

***

```{r}
tree('ornithischia', collapse='none')
```

***

```{r}
tree('sauropoda', collapse='none')
```

***

```{r}
tree('tyrannosauroidea', collapse='avialae', xmin=-173)
```



