---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  message = FALSE
)
```

# arboretum

<!-- badges: start -->
<!-- badges: end -->

Plot customised phylogentic trees.

## Installation

You can install the development version of arboretum from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("dkidney/arboretum")
```

## Examples

Load the package (and check the version)

```{r}
library(arboretum)
packageVersion("arboretum")
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(
	fig.asp = 0.6, 
	fig.width = 15, 
	out.width = "100%"
)
```

Plot the default tree. By default, any branch node ending in '-ae', '-morpha' or '-formes' will be collapsed.

```{r}
tree()
```

Use the `taxon` argument to create a tree for a specific taxon, using the default rule for collapsing branches.

```{r}
 tree(taxon = 'dinosauria')
```

Use the `collapse` argument to choose which branches in the tree are collapsed.

```{r}
tree(taxon = 'dinosauria',
	 collapse = c('sauropodomorpha',
	 			 'ornithopoda',
	 			 'theropoda',
	 			 'ankylosauria',
	 			 'stegosauria',
	 			 'pachycephalosauria',
	 			 'ceratopsia'))
```

Use `collapse='none'` to see all available branches.

```{r}
tree(taxon='sauropoda', collapse='none')
```

Other example trees:

```{r}
tree('tetanurae', collapse='avialae')
```

```{r}
tree('sauropterygia', collapse='none')
```

```{r}
tree('synapsida')
```

```{r}
tree('pseudosuchia', collapse='none')
```
